\normalfont \normalsize \textsc{University of Stuttgart} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Hauptseminar:\\The Logjam Attack \\ \horrule{2pt} \\[0.5cm]

### 2017-06-07 Ausarbeitung/paper.tex
precomputation for NFS finished

\subsubsection{Smoothness Assumption}
Define that an integer number $x$ is $B$-smooth, if all prime factors of $x$ are smaller that $B$. NFS assumes the base $\alpha$ to be $B$-smooth where $B$ is a upper bound for the prime values in the factor base (which is the output of the precomputation). If $\alpha$ is not $B$-smooth, we can use a $B$-smooth $\alpha'$ instead. Then, we can compute $\log_{\alpha'}\alpha$ and transform back to the original problem with
\begin{equation}
\log_\alpha D\equiv\frac{\log_{\alpha'}D}{\log_{\alpha'}\alpha}\mod (q-1)
\text{ .}
\end{equation}
If $\alpha'$ is not a generator for $\mathrm{GF}(q)^*$, the logs on the right hand side might not exist. $\alpha'$ can be checked for feasibility by factoring $(q-1)$ with the NFS factoring algorithm and check
\begin{equation}
(a')^{\frac{q-1}{p}} \not\equiv 1 \mod q,\quad\forall p\parallel q
\text{ ,}
\end{equation}
where $p\parallel q$ denotes that $p$ is a prime divisor of $q$. The reason why $\alpha'$ needs to be $B$-Smooth is that the factor base needs to have at least one inhomogeneous relation for the logs of the factor base, using the equation
\begin{eqnarray}
log_\alpha\alpha = 1 \equiv \sum_{p^t\parallel a}t\log_\alpha p \mod (q-1)
\text{ ,}
\end{eqnarray}
otherwise we gain no knowledge from the factor base.

@@

\subsubsection{Sieving}

@@

>>>>

\subsubsection{Smoothness Assumption}
Define that an integer number $x$ is $B$-smooth, if all prime factors of $x$ are smaller that $B$. NFS assumes the base $\alpha$ to be $B$-smooth where $B$ is a upper bound for the prime values in the factor base (which is the output of the precomputation). If $\alpha$ is not $B$-smooth, we can use a $B$-smooth $\alpha'$ instead. Then, we can compute $\log_{\alpha'}\alpha$ and transform back to the original problem with
\begin{equation}
\log_\alpha D\equiv\frac{\log_{\alpha'}D}{\log_{\alpha'}\alpha}\mod (q-1)
\text{ .}
\end{equation}
If $\alpha'$ is not a generator for $\mathrm{GF}(q)^*$, the logs on the right hand side might not exist. $\alpha'$ can be checked for feasibility by factoring $(q-1)$ with the NFS factoring algorithm and check
\begin{equation}
(a')^{\frac{q-1}{p}} \not\equiv 1 \mod q,\quad\forall p\parallel q
\text{ ,}
\end{equation}
where $p\parallel q$ denotes that $p$ is a prime divisor of $q$. The reason why $\alpha'$ needs to be $B$-Smooth is that the factor base needs to have at least one inhomogeneous relation for the logs of the factor base, using the equation
\begin{eqnarray}
\label{eqn:assumption}
\log_\alpha\alpha = 1 \equiv \sum_{p^t\parallel a}t\log_\alpha p \mod (q-1)
\text{ ,}
\end{eqnarray}
otherwise we gain no knowledge from the factor base.

@@

\subsubsection{Sieving}
In this step we try to find linear equations that are informative in a sense that they are related to the the logarithms in $\mathcal{B}$. For that, sieve through integer pairs $(c,d)$ that are co-prime for which $c+dm$ and $c+d\gamma$ are $S$-smooth where $S = \prod_{s\in\mathcal{B}_\mathbb{Q}}$. For this smoothness criteria, we can formulate equations
\begin{eqnarray}
c+dm = \prod_{s\in\mathcal{B}_\mathbb{Q}}s^{w_s(c,d)}
\end{eqnarray}
and
\begin{eqnarray}
|N(c+d\gamma)| = \prod_{s\in\mathcal{B}_\mathbb{Q}}s^{v_s(c,d)}
\text{ ,}
\end{eqnarray}
where $N(c+d\gamma) = (-d)^kf(-\frac{c}{d})$ (see original paper \citep{gordon1993discrete} for explanation), for some $w_s,v_s\in\mathbb{Z}^+$.

From here we can derive factorizations for primes in $\mathcal{B}_K$ with the fact (not proven here) that there is an unique ideal $\hat{s}\in\mathcal{B}_K$ lying over $s$ and dividing $c+d\gamma$. Let $v_{\hat{S}}(c,d) = v_s(c,d)$ for this ideal and be zero for other ideals in $\mathcal{B}_K$ of norm $s$. Then we have the following
\begin{eqnarray}
\label{eqnSieve1}
c+dm = \prod_{s\in\mathcal{B}_\mathbb{Q}}s^{w_s(c,d)}
\end{eqnarray}
and
\begin{eqnarray}
\label{eqnSieve2}
c+d\gamma = \prod_{\hat{s}\in\mathcal{B}_K}\hat{s}^{v_{\hat{s}}(c,d)}
\text{ .}
\end{eqnarray}
We repeats the steps described so far, which means, try to find more pairs $(c,d)$ to build equations \ref{eqnSieve1} and \ref{eqnSieve2} until we have at least $|\mathcal{B}|$ of these equations. These are now used to form a large matrix $A$, where its rows are the $w_s$'s and $v_{\hat{s}}$'s for each equation. From $A$ we extract only those columns where elements are in $\mathcal{B}-\mathcal{B}'$, forming a new matrix $A'$. This means, we are only interested in solutions for primes $s\in\mathcal{B}'$. $A'$ is now the input for the next stage.

@@

\subsubsection{Results}
Here I sum up the final result not showing details, as it needs more technical preparations that I neglected for simplicity. Feel free to look at the original paper for a complete derivation of the solution.

After applying the algorithm described in the Linear Algebra step on the matrix resulted form the Sieving step, we have some new equations
\begin{equation}
\prod_{(c,d)}(c+dm)^{x(c,d)} = U
\textit{ ,}
\end{equation}
where $x(c,d)$ are some newly computed integers and $U$ is a unit in $O_K$. After some intermediate steps, we can express the logs of primes $s\in\mathcal{B}$ as $z_s$ (which is here a black box) and state
\begin{equation}
\prod_{s\in\mathcal{B}'}s^{z_s}\equiv 1\mod q
\text{ .}
\end{equation}
Taking the log, we have
\begin{equation}
\sum_{s\in\mathcal{B}'}\log_\alpha s \equiv 0 \mod (q-1)
\text{ .}
\end{equation}
With more than $|\mathcal{B}'|$ such congruences, we can solve these with equation \ref{eqn:assumption} and obtain the logs for all primes $s\in\mathcal{B}'$.
